### 2023-01-17 output/summary_statistics/tables/summary_statistics.tex
Updated Zestimates in summary statistics

\begin{tabular}{llcccc}
\toprule
 &  & Mean & Median & S.D. & N \\
Panel & Variable &  &  &  &  \\
\midrule
\multirow[c]{3}{3cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.00 & 0.33 & 40,727 \\
 & No cause & 0.11 & 0.00 & 0.31 & 40,727 \\
 & Non-payment of rent & 0.75 & 1.00 & 0.43 & 40,727 \\
\cline{1-6}
\multirow[c]{6}{3cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.20 & 0.00 & 0.40 & 40,727 \\
 & Case dismised & 0.29 & 0.00 & 0.45 & 40,727 \\
 & Case duration & 57.81 & 21.00 & 78.29 & 39,087 \\
 & Case heard & 0.06 & 0.00 & 0.23 & 40,727 \\
 & Case mediated & 0.41 & 0.00 & 0.49 & 40,727 \\
 & Money judgment & 1,890.34 & 0.00 & 5,279.49 & 40,727 \\
\cline{1-6}
\multirow[c]{4}{3cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.00 & 0.28 & 40,727 \\
 & Defendant is an entity & 0.01 & 0.00 & 0.08 & 40,727 \\
 & Plaintiff has an attorney & 0.84 & 1.00 & 0.37 & 40,727 \\
 & Plaintiff is an entity & 0.70 & 1.00 & 0.46 & 40,727 \\
\cline{1-6}
\multirow[c]{4}{3cm}{\textit{Panel D: Assessor Records}} & Building value & 8,350,204.19 & 636,500.00 & 22,073,916.94 & 36,587 \\
 & Land value & 2,471,065.61 & 192,400.00 & 6,218,383.08 & 36,587 \\
 & Other value & 112,575.80 & 1,000.00 & 659,661.29 & 36,587 \\
 & Total property value & 10,900,678.30 & 954,900.00 & 26,482,630.60 & 36,587 \\
\cline{1-6}
\multirow[c]{3}{3cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,659.44 & 47,105.00 & 27,177.48 & 40,726 \\
 & Population density (2010) & 9,159.77 & 5,978.61 & 9,574.14 & 40,726 \\
 & Portion white (2010) & 0.58 & 0.63 & 0.29 & 40,726 \\
\cline{1-6}
\multirow[c]{9}{3cm}{\textit{Panel F: Zestimates Around Filing Date}} & Filing date & 377,384.02 & 305,144.00 & 316,645.29 & 10,096 \\
 & Five years before filing date & 261,462.86 & 213,270.60 & 238,040.64 & 9,842 \\
 & Four years before filing date & 280,243.32 & 225,065.75 & 276,051.45 & 9,968 \\
 & One year after filing date & 421,601.75 & 347,550.00 & 344,328.86 & 10,443 \\
 & One year before filing date & 351,172.05 & 278,722.25 & 311,982.74 & 10,190 \\
 & Three years after filing date & 501,611.80 & 414,600.00 & 780,467.01 & 5,894 \\
 & Three years before filing date & 307,137.16 & 240,097.38 & 369,763.53 & 10,172 \\
 & Two years after filing date & 477,948.08 & 393,900.00 & 457,694.83 & 9,175 \\
 & Two years before filing date & 341,084.08 & 259,176.00 & 987,145.51 & 10,182 \\
\cline{1-6}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcccc}
\toprule
 &  & Mean & Median & S.D. & N \\
Panel & Variable &  &  &  &  \\
\midrule
\multirow[c]{3}{3cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.00 & 0.33 & 40,727 \\
 & No cause & 0.11 & 0.00 & 0.31 & 40,727 \\
 & Non-payment of rent & 0.75 & 1.00 & 0.43 & 40,727 \\
\cline{1-6}
\multirow[c]{6}{3cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.20 & 0.00 & 0.40 & 40,727 \\
 & Case dismised & 0.29 & 0.00 & 0.45 & 40,727 \\
 & Case duration & 57.81 & 21.00 & 78.29 & 39,087 \\
 & Case heard & 0.06 & 0.00 & 0.23 & 40,727 \\
 & Case mediated & 0.41 & 0.00 & 0.49 & 40,727 \\
 & Money judgment & 1,890.34 & 0.00 & 5,279.49 & 40,727 \\
\cline{1-6}
\multirow[c]{4}{3cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.00 & 0.28 & 40,727 \\
 & Defendant is an entity & 0.01 & 0.00 & 0.08 & 40,727 \\
 & Plaintiff has an attorney & 0.84 & 1.00 & 0.37 & 40,727 \\
 & Plaintiff is an entity & 0.70 & 1.00 & 0.46 & 40,727 \\
\cline{1-6}
\multirow[c]{3}{3cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,659.44 & 47,105.00 & 27,177.48 & 40,726 \\
 & Population density (2010) & 9,159.77 & 5,978.61 & 9,574.14 & 40,726 \\
 & Portion white (2010) & 0.58 & 0.63 & 0.29 & 40,726 \\
\cline{1-6}
\multirow[c]{2}{3cm}{\textit{Panel F: Pretreatment Zestimates}} & Change from Jan. 2018 to Jan. 2019 & 22,601.20 & 15,786.00 & 74,245.92 & 10,170 \\
 & Jan. 2018 & 322,775.21 & 256,528.00 & 298,417.63 & 10,177 \\
\cline{1-6}
\bottomrule
\end{tabular}
